Stack Safety as a Security Property

### 2020-07-08 main.tex
Note on the StkTokens proof technique

>>>>

\rb{As far as I can tell, while their notion of components and interfaces seems
  standard, observable behavior appears to be limited to cotermination. The
  previous paper makes explicit that (at least at that point) they are not
  interested in externally observable side effects like console output or memory
  access traces.}
